Robust self-testing of large entanglement with constant alphabet

### 2019-04-26 Draft/draft.tex
Honghao: small modification
Honghao: writing section 6.1

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}

% Probabilities
\newcommand{\pr}[2]{P(#1|#2)}
\newcommand{\pa}[2]{P_A(#1|#2)}
\newcommand{\pb}[2]{P_B(#1|#2)}

@@

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
\carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\carl{Make this clear in the definition itself.}
\hf{I made the definition of the scoring function part of the big definition now.}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.

@@

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
The weighted CHSH inequality is true 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $M_1 = \pauliz$, $M_2 = \paulix$,
	$N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

%The main contribution of our work is the construction of a correlation, which is the combination of 
%the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
%and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
%know yet what a linear system game is, so this comment is more confusing than helpful.}
%The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
%primitive root. 
%In the next part, we introduce the definition of self-testing, the definition of linear system game, 
%and its operator solution, 
%following definitions given in Ref.~\cite{coladan2017, slofstra2017}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}
%\begin{definition}[Self-testing]
%	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
%	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
%	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
%	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
%	such that 	
%	\begin{align*}
%		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
%	\end{align*}
%\end{definition}

@@

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.

@@

\begin{definition}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ c = (i,j,k) \in C(r)$:
\begin{align}
	&h_{jk}b_j c_k = e\\
	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
\end{align}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square test:
\begin{align}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

@@

Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

@@

\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{Proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$.
The decompositions allow us to determine some key relations between Alice and Bob's observables
and their shared state, which will be used to draw the closeness conclusion.

\begin{proof}
The first step is to find a sum-of-square decomposition of 
the following Bell expression
\begin{align}
	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_1B_1+A_1B_2) -  A_2B_1 + A_2B_2.
\end{align} 
With the following notation
\begin{align*}
	&Z_A = A_1 && X_A = A_2\\
	&Z_B = \frac{B_1+B_2}{2\cos(\mu)} && X_B = \frac{B_1-B_2}{2\sin(\mu)},
\end{align*}
the two SOS decompositions that we use are
\begin{align}
	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
\end{align}
The verification is omitted here.

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}

% Probabilities
\newcommand{\pr}[2]{P(#1|#2)}
\newcommand{\pa}[2]{P_A(#1|#2)}
\newcommand{\pb}[2]{P_B(#1|#2)}
\newcommand{\tpr}[2]{\tilde{P}(#1|#2)}

@@

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
\carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\carl{Make this clear in the definition itself.}
\hf{I made the definition of the scoring function part of the big definition now.}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.

@@

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
The weighted CHSH inequality is true 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}

@@

@@

\begin{definition}
\label{def:gamma}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ c = (i,j,k) \in C(r)$:
\begin{align}
	&h_{jk}b_j c_k = e\\
	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
\end{align}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square test:
\begin{align}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

@@

Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	\label{eq:w_subspace}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

@@

\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{The proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$,
where $\I_\alpha$ is expressed in terms of $\{M_x\}$ and $\{N_y\}$.
The decompositions allow us to determine some key relations between Alice and Bob's observables
and their shared state, which will be used to draw the conclusion.
